MATH 245 Homework 2

### 2024-02-23 PDEs/math245_hw2.Rmd
started pde hw3

First, define $w(t,x)=u(t,x)-H(t)$, where $H_x(t)=h(t)$.

Then our IBVP becomes:
\begin{equation*}
    \begin{cases}
      \square w= \square u - H''(t)=f(t,x)-H''(t) \equiv F(t,x) & x \geq 0, t>0\\
      w(0,x)=u(0,x)-H(0)=\phi(x) - H(0) \equiv \Phi(x) & x \geq 0\\
      w_t(0,x) =  u_t(0,x)  - H_t(0)= \psi(x) - H_t(0) \equiv \Psi(x) & x \geq 0\\
      w_x(0,x) = u_x(t,0) - H_x(0)= u_x(t,0)-h(t) \equiv 0 & t \geq 0
    \end{cases}       
\end{equation*}

@@

\begin{equation*} 
\begin{cases}
w_{tt}=c^2 w_{rr} \\
u(0,r)=0 \\
u_t(0,r) = \begin{cases}
  1  & \lvert{r}\rvert \leq 1 \\
  0 &  \lvert{r}\rvert > 1
  \end{cases}
\end{cases}
\end{equation*}

So can use d'Alembert's formula to find the solution:
 $$w(t,r)= \frac{\varphi(r+ct)+\varphi(r-ct)}{2}+\frac{1}{2c} \int_{r-ct}^{r+ct}{\psi(s)ds}$$
 Since $\varphi=0$, 
 $$w(t,r)= \frac{1}{2c} \int_{r-ct}^{r+ct}{\psi(s)ds}$$

>>>>

First, define $w(t,x)=u(t,x)-H(t)$, where $H'(t)=h(t)$.

Then our IBVP becomes:
\begin{equation*}
    \begin{cases}
      \square w= \square u - H''(t)=f(t,x)-H''(t) \equiv F(t,x) & x \geq 0, t>0\\
      w(0,x)=u(0,x)-H(0)=\phi(x) - H(0) \equiv \Phi(x) & x \geq 0\\
      w_t(0,x) =  u_t(0,x)  - H'(0)= \psi(x) - H'(0) \equiv \Psi(x) & x \geq 0\\
      w_x(0,x) = u_x(t,0) - H'(0)= u_x(t,0)-h(t) \equiv 0 & t \geq 0
    \end{cases}       
\end{equation*}

@@

\begin{equation*} 
\begin{cases}
w_{tt}=c^2 w_{rr} & t>0, \, r \geq 0\\
u(0,r)=0 & r \geq 0\\
u_t(0,r) = \begin{cases}
  1  & \lvert{r}\rvert \leq 1 \\
  0 &  \lvert{r}\rvert > 1
  \end{cases} & r \geq 0\\
\end{cases}
\end{equation*}

Although $r$ is nonnegative, since $\varphi=0$ and there are absolute value bars in $\phi$, we can safely use d'Alembert's formula to find the solution:
 $$w(t,r)= \frac{\varphi(r+ct)+\varphi(r-ct)}{2}+\frac{1}{2c} \int_{r-ct}^{r+ct}{\psi(s)ds}$$
 Since $\varphi=0$, 
 $$w(t,r)= \frac{1}{2c} \int_{r-ct}^{r+ct}{\psi(s)ds}$$
